The benefits of reporting critical effect size values\footnote{The manuscript as been posted as a pre-print and has not yet undergone peer-review.}

### 2025-02-24 paper/paper.Rmd
adding equations table

bibliography      : "bibliography.bib"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

@@

>>>>

bibliography      : "bibliography.bib"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

@@

\bfilippo
Table \@ref(tab:eqsummary) summarises the equations presented above.

```{r eqsummary, echo=FALSE, tab.cap="Summary of the critical effect size equations."}
library(kableExtra)

eqs <- data.frame(
  stringsAsFactors = FALSE,
             Model = c("One-sample t-test",
                       "Paired t-test","Paired t-test","Between-sample t-test",
                       "Correlation","Correlation","Meta-analysis/Regression"),
         Numerator = c("$b_c = t_c \\times \\mbox{SE}_b$","$b_c = t_c \\times \\mbox{SE}_b$",
                       "$b_{z_c} = t_c \\times \\mbox{SE}_b$",
                       "$b_c = t_c \\times \\mbox{SE}_b$",
                       "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
                       "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$"),
       Denominator = c("$s$", NA, "$s_D$", "$s_p$", NA, NA, NA),
          Equation = c("$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s}$",
                       "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p}$",
                       "$d_{z_c} = \\frac{t_c \\times \\mbox{SE}_b}{s_D}$",
                       "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p}$",
                       "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
                       "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$")
)

eqs |> 
  dplyr::select(Model, Equation) |> 
  kable(escape = FALSE,
        booktabs = TRUE) |> 
  collapse_rows(1) |> 
  kable_styling(latex_options = "HOLD_position") |> 
  row_spec(0, bold = TRUE)
```

\efilippo

### 2025-02-24 paper/paper.tex
^^
adding equations table

  man]{apa7}

@@

  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}

@@

  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{critical effect size values, statistical significance, hypothesis testing, effect sizes\newline\indent Word count: 4761}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother
\usepackage{xcolor}
\newcommand{\bfilippo}{\color{blue}}
\newcommand{\efilippo}{\color{black}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The benefits of reporting critical effect size values},
  pdfauthor={Ambra Perugini1, Filippo Gambarota1, Enrico Toffalini2, Daniël Lakens3, Massimiliano Pastore1, Livio Finos4, Psicostat1, \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={critical effect size values, statistical significance, hypothesis testing, effect sizes},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The benefits of reporting critical effect size values}
\author{Ambra Perugini\textsuperscript{1}, Filippo Gambarota\textsuperscript{1}, Enrico Toffalini\textsuperscript{2}, Daniël Lakens\textsuperscript{3}, Massimiliano Pastore\textsuperscript{1}, Livio Finos\textsuperscript{4}, Psicostat\textsuperscript{1}, \& Gianmarco Altoè\textsuperscript{1}}
\date{}

@@

\hypertarget{small-sample-sizes-and-uncertain-sample-size-setermination}{%
\subsection{Small Sample Sizes and Uncertain Sample Size Setermination}\label{small-sample-sizes-and-uncertain-sample-size-setermination}}

@@

\hypertarget{large-sample-sizes-and-meta-analysis}{%
\subsection{Large Sample Sizes and Meta-analysis}\label{large-sample-sizes-and-meta-analysis}}

@@

\hypertarget{how-to-compute-critical-effect-size-values}{%
\section{How to Compute Critical Effect Size Values}\label{how-to-compute-critical-effect-size-values}}

@@

\hypertarget{t-test}{%
\subsection{\texorpdfstring{\(t\)-test}{t-test}}\label{t-test}}

@@

\hypertarget{one-sample-t-test}{%
\subsubsection{\texorpdfstring{One sample \(t\)-test}{One sample t-test}}\label{one-sample-t-test}}

@@

\hypertarget{two-sample-t-test}{%
\subsubsection{\texorpdfstring{Two-sample \(t\)-test}{Two-sample t-test}}\label{two-sample-t-test}}

@@

\hypertarget{paired-sample-t-test}{%
\subsubsection{\texorpdfstring{Paired sample \(t\)-test}{Paired sample t-test}}\label{paired-sample-t-test}}

@@

\hypertarget{hedgess-correction}{%
\subsubsection{Hedges's correction}\label{hedgess-correction}}

@@

\hypertarget{linear-regression}{%
\subsection{Linear Regression}\label{linear-regression}}

@@

\hypertarget{meta-analysis}{%
\subsection{Meta-analysis}\label{meta-analysis}}

@@

\hypertarget{other-models}{%
\subsection{Other models}\label{other-models}}

@@

\hypertarget{examples-in-r}{%
\section{Examples in R}\label{examples-in-r}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altoe2020enhancing}{}}%
Altoè, G., Bertoldo, G., Zandonella Callegher, C., Toffalini, E., Calcagnı̀, A., Finos, L., \& Pastore, M. (2020). Enhancing statistical inference in psychological research via prospective and retrospective design analysis. \emph{Frontiers in Psychology}, \emph{10}, 499756.

\leavevmode\vadjust pre{\hypertarget{ref-Borenstein2009-mo}{}}%
Borenstein, M., Hedges, L. V., Higgins, J. P. T., \& Rothstein, H. R. (2009). \emph{Introduction to {Meta-Analysis}}. \url{https://doi.org/10.1002/9780470743386}

\leavevmode\vadjust pre{\hypertarget{ref-Bowley1928-yt}{}}%
Bowley, A. L. (1928). The standard deviation of the correlation coefficient. \emph{Journal of the American Statistical Association}, \emph{23}, 31. \url{https://doi.org/10.2307/2277400}

\leavevmode\vadjust pre{\hypertarget{ref-byers2020building}{}}%
Byers-Heinlein, K., Bergmann, C., Davies, C., Frank, M. C., Hamlin, J. K., Kline, M., Kominsky, J. F., Kosie, J. E., Lew-Williams, C., Liu, L., et al. (2020). Building a collaborative psychological science: Lessons learned from ManyBabies 1. \emph{Canadian Psychology/Psychologie Canadienne}, \emph{61}(4), 349.

\leavevmode\vadjust pre{\hypertarget{ref-chow1988significance}{}}%
Chow, S. L. (1988). Significance test or effect size? \emph{Psychological Bulletin}, \emph{103}(1), 105.

\leavevmode\vadjust pre{\hypertarget{ref-cohen1994}{}}%
Cohen, J. (1994). The earth is round (p \textless{} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003.

\leavevmode\vadjust pre{\hypertarget{ref-cortina1997logic}{}}%
Cortina, J. M., \& Dunlap, W. P. (1997). On the logic and purpose of significance testing. \emph{Psychological Methods}, \emph{2}(2), 161.

\leavevmode\vadjust pre{\hypertarget{ref-Fisher1915-ks}{}}%
Fisher, R. A. (1915). Frequency distribution of the values of the correlation coefficient in samples from an indefinitely large population. \emph{Biometrika}, \emph{10}, 507. \url{https://doi.org/10.2307/2331838}

\leavevmode\vadjust pre{\hypertarget{ref-Fisher1921-qz}{}}%
Fisher, R. A. (1921). On the "probable error" of a coefficient of correlation deduced from a small sample. \emph{Metron}.

\leavevmode\vadjust pre{\hypertarget{ref-funder2019evaluating}{}}%
Funder, D. C., \& Ozer, D. J. (2019). Evaluating effect size in psychological research: Sense and nonsense. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(2), 156--168.

\leavevmode\vadjust pre{\hypertarget{ref-Gelman2008-zp}{}}%
Gelman, A. (2008). Scaling regression inputs by dividing by two standard deviations. \emph{Statistics in Medicine}, \emph{27}, 2865--2873. \url{https://doi.org/10.1002/sim.3107}

\leavevmode\vadjust pre{\hypertarget{ref-gigerenzer2004null}{}}%
Gigerenzer, G., Krauss, S., \& Vitouch, O. (2004). The null ritual. \emph{The Sage Handbook of Quantitative Methodology for the Social Sciences}, 391--408.

\leavevmode\vadjust pre{\hypertarget{ref-Gross2023-fl}{}}%
Groß, J., \& Möller, A. (2023). A note on cohen's d from a partitioned linear regression model. \emph{Journal of Statistical Theory and Practice}, \emph{17}. \url{https://doi.org/10.1007/s42519-023-00323-w}

\leavevmode\vadjust pre{\hypertarget{ref-hagen1997praise}{}}%
Hagen, R. L. (1997). \emph{In praise of the null hypothesis statistical test.}

\leavevmode\vadjust pre{\hypertarget{ref-haig2017tests}{}}%
Haig, B. D. (2017). Tests of statistical significance made sound. \emph{Educational and Psychological Measurement}, \emph{77}(3), 489--506.

\leavevmode\vadjust pre{\hypertarget{ref-Hedges1981-za}{}}%
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{6}, 107--128. \url{https://doi.org/10.3102/10769986006002107}

\leavevmode\vadjust pre{\hypertarget{ref-hedges1984estimation}{}}%
Hedges, L. V. (1984). Estimation of effect size under nonrandom sampling: The effects of censoring studies yielding statistically insignificant mean differences. \emph{Journal of Educational Statistics}, \emph{9}(1), 61--85.

\leavevmode\vadjust pre{\hypertarget{ref-jarke2022roadmap}{}}%
Jarke, H., Anand-Vembar, S., Alzahawi, S., Andersen, T. L., Bojanić, L., Carstensen, A., Feldman, G., Garcia-Garzon, E., Kapoor, H., Lewis, S., et al. (2022). A roadmap to large-scale multi-country replications in psychology. \emph{Collabra: Psychology}, \emph{8}(1), 57538.

\leavevmode\vadjust pre{\hypertarget{ref-kramer2014experimental}{}}%
Kramer, A. D., Guillory, J. E., \& Hancock, J. T. (2014). Experimental evidence of massive-scale emotional contagion through social networks. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{111}(24), 8788.

\leavevmode\vadjust pre{\hypertarget{ref-krueger2001null}{}}%
Krueger, J. (2001). Null hypothesis significance testing: On the survival of a flawed method. \emph{American Psychologist}, \emph{56}(1), 16.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2013calculating}{}}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}, 62627.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2021practical}{}}%
Lakens, D. (2021). The practical alternative to the p value is the correctly used p value. \emph{Perspectives on Psychological Science}, \emph{16}(3), 639--648.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2022sample}{}}%
Lakens, D. (2022). Sample size justification. \emph{Collabra: Psychology}, \emph{8}(1), 33267.

\leavevmode\vadjust pre{\hypertarget{ref-miller2017hypothesis}{}}%
Miller, J. (2017). Hypothesis testing in the real world. \emph{Educational and Psychological Measurement}, \emph{77}(4), 663--672.

\leavevmode\vadjust pre{\hypertarget{ref-morris2002combining}{}}%
Morris, S. B., \& DeShon, R. P. (2002). Combining effect size estimates in meta-analysis with repeated measures and independent-groups designs. \emph{Psychological Methods}, \emph{7}(1), 105.

\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018psychological}{}}%
Moshontz, H., Campbell, L., Ebersole, C. R., IJzerman, H., Urry, H. L., Forscher, P. S., Grahe, J. E., McCarthy, R. J., Musser, E. D., Antfolk, J., et al. (2018). The psychological science accelerator: Advancing psychology through a distributed collaborative network. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.

\leavevmode\vadjust pre{\hypertarget{ref-nickerson2000null}{}}%
Nickerson, R. S. (2000). Null hypothesis significance testing: A review of an old and continuing controversy. \emph{Psychological Methods}, \emph{5}(2), 241.

\leavevmode\vadjust pre{\hypertarget{ref-orben_crud_2020}{}}%
Orben, A., \& Lakens, D. (2020). Crud ({Re}){Defined}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(2), 238--247. \url{https://doi.org/10.1177/2515245920917961}

\leavevmode\vadjust pre{\hypertarget{ref-Satterthwaite1946-aq}{}}%
Satterthwaite, F. E. (1946). An approximate distribution of estimates of variance components. \emph{Biometrics Bulletin}, \emph{2}, 110. \url{https://doi.org/10.2307/3002019}

\leavevmode\vadjust pre{\hypertarget{ref-sirois2023pupil}{}}%
Sirois, S., Brisson, J., Blaser, E., Calignano, G., Donenfeld, J., Hepach, R., Hochmann, J.-R., Kaldy, Z., Liszkowski, U., Mayer, M., et al. (2023). The pupil collaboration: A multi-lab, multi-method analysis of goal attribution in infants. \emph{Infant Behavior and Development}, \emph{73}, 101890.

\leavevmode\vadjust pre{\hypertarget{ref-szucs2017empirical}{}}%
Szucs, D., \& Ioannidis, J. P. (2017). Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature. \emph{PLoS Biology}, \emph{15}(3), e2000797.

\leavevmode\vadjust pre{\hypertarget{ref-transue2019apa}{}}%
Transue, B. (2019). \emph{APA style 7th edition}.

\leavevmode\vadjust pre{\hypertarget{ref-Viechtbauer2007-tq}{}}%
Viechtbauer, W. (2007). Approximate confidence intervals for standardized effect sizes in the two-independent and two-dependent samples design. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{32}, 39--60. \url{https://doi.org/10.3102/1076998606298034}

\leavevmode\vadjust pre{\hypertarget{ref-weiss2014spatial}{}}%
Weiss, A. H., Biron, T., Lieder, I., Granot, R. Y., \& Ahissar, M. (2014). Spatial vision is superior in musicians when memory plays a role. \emph{Journal of Vision}, \emph{14}(9), 18--18.

\leavevmode\vadjust pre{\hypertarget{ref-Welch1947-wh}{}}%
Welch, B. L. (1947). The generalization of {``student's''} problem when several different population variances are involved. \emph{Biometrika}, \emph{34}, 28. \url{https://doi.org/10.2307/2332510}

\leavevmode\vadjust pre{\hypertarget{ref-wilson2020science}{}}%
Wilson, B. M., Harris, C. R., \& Wixted, J. T. (2020). Science is not a signal detection problem. \emph{Proceedings of the National Academy of Sciences}, \emph{117}(11), 5559--5567.

>>>>

  man,floatsintext]{apa7}

@@

  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}

@@

  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{critical effect size values, statistical significance, hypothesis testing, effect sizes\newline\indent Word count: 4761}
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother
\usepackage{xcolor}
\newcommand{\bfilippo}{\color{blue}}
\newcommand{\efilippo}{\color{black}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The benefits of reporting critical effect size values},
  pdfauthor={Ambra Perugini1, Filippo Gambarota1, Enrico Toffalini2, Daniël Lakens3, Massimiliano Pastore1, Livio Finos4, Psicostat1, \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={critical effect size values, statistical significance, hypothesis testing, effect sizes},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The benefits of reporting critical effect size values\footnote{The manuscript as been posted as a pre-print and has not yet undergone peer-review.}}
\author{Ambra Perugini\textsuperscript{1}, Filippo Gambarota\textsuperscript{1}, Enrico Toffalini\textsuperscript{2}, Daniël Lakens\textsuperscript{3}, Massimiliano Pastore\textsuperscript{1}, Livio Finos\textsuperscript{4}, Psicostat\textsuperscript{1}, \& Gianmarco Altoè\textsuperscript{1}}
\date{}

@@

\subsection{Small Sample Sizes and Uncertain Sample Size Setermination}\label{small-sample-sizes-and-uncertain-sample-size-setermination}

@@

\subsection{Large Sample Sizes and Meta-analysis}\label{large-sample-sizes-and-meta-analysis}

@@

\section{How to Compute Critical Effect Size Values}\label{how-to-compute-critical-effect-size-values}

@@

\subsection{\texorpdfstring{\(t\)-test}{t-test}}\label{t-test}

@@

\subsubsection{\texorpdfstring{One sample \(t\)-test}{One sample t-test}}\label{one-sample-t-test}

@@

\subsubsection{\texorpdfstring{Two-sample \(t\)-test}{Two-sample t-test}}\label{two-sample-t-test}

@@

\subsubsection{\texorpdfstring{Paired sample \(t\)-test}{Paired sample t-test}}\label{paired-sample-t-test}

@@

\subsubsection{Hedges's correction}\label{hedgess-correction}

@@

\subsection{Linear Regression}\label{linear-regression}

@@

\subsection{Meta-analysis}\label{meta-analysis}

@@

\subsection{Other models}\label{other-models}

@@

\color{blue}

Table \ref{tab:eqsummary} summarises the equations presented above.

\begin{table}[H]

\caption{\label{tab:eqsummary}Summary of the critical effect size equations.}
\centering
\begin{tabular}[t]{ll}
\toprule
\textbf{Model} & \textbf{Equation}\\
\midrule
One-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s}$\\
\cmidrule{1-2}
 & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p}$\\
\cmidrule{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Paired t-test} & $d_{z_c} = \frac{t_c \times \mbox{SE}_b}{s_D}$\\
\cmidrule{1-2}
Between-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p}$\\
\cmidrule{1-2}
 & $r_c = \frac{t_c}{\sqrt{n - 2 + t^2_c}}$\\
\cmidrule{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Correlation} & $r_{z_c} = \frac{z_c}{\sqrt{n - 3}}$\\
\cmidrule{1-2}
Meta-analysis/Regression & $\beta_c = t_c \times \mbox{SE}_{\beta}$\\
\bottomrule
\end{tabular}
\end{table}

\color{black}

\section{Examples in R}\label{examples-in-r}

@@

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-altoe2020enhancing}
Altoè, G., Bertoldo, G., Zandonella Callegher, C., Toffalini, E., Calcagnı̀, A., Finos, L., \& Pastore, M. (2020). Enhancing statistical inference in psychological research via prospective and retrospective design analysis. \emph{Frontiers in Psychology}, \emph{10}, 499756.

\bibitem[\citeproctext]{ref-Borenstein2009-mo}
Borenstein, M., Hedges, L. V., Higgins, J. P. T., \& Rothstein, H. R. (2009). \emph{Introduction to {Meta-Analysis}}. \url{https://doi.org/10.1002/9780470743386}

\bibitem[\citeproctext]{ref-Bowley1928-yt}
Bowley, A. L. (1928). The standard deviation of the correlation coefficient. \emph{Journal of the American Statistical Association}, \emph{23}, 31. \url{https://doi.org/10.2307/2277400}

\bibitem[\citeproctext]{ref-byers2020building}
Byers-Heinlein, K., Bergmann, C., Davies, C., Frank, M. C., Hamlin, J. K., Kline, M., Kominsky, J. F., Kosie, J. E., Lew-Williams, C., Liu, L., et al. (2020). Building a collaborative psychological science: Lessons learned from ManyBabies 1. \emph{Canadian Psychology/Psychologie Canadienne}, \emph{61}(4), 349.

\bibitem[\citeproctext]{ref-chow1988significance}
Chow, S. L. (1988). Significance test or effect size? \emph{Psychological Bulletin}, \emph{103}(1), 105.

\bibitem[\citeproctext]{ref-cohen1994}
Cohen, J. (1994). The earth is round (p \textless{} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003.

\bibitem[\citeproctext]{ref-cortina1997logic}
Cortina, J. M., \& Dunlap, W. P. (1997). On the logic and purpose of significance testing. \emph{Psychological Methods}, \emph{2}(2), 161.

\bibitem[\citeproctext]{ref-Fisher1915-ks}
Fisher, R. A. (1915). Frequency distribution of the values of the correlation coefficient in samples from an indefinitely large population. \emph{Biometrika}, \emph{10}, 507. \url{https://doi.org/10.2307/2331838}

\bibitem[\citeproctext]{ref-Fisher1921-qz}
Fisher, R. A. (1921). On the "probable error" of a coefficient of correlation deduced from a small sample. \emph{Metron}.

\bibitem[\citeproctext]{ref-funder2019evaluating}
Funder, D. C., \& Ozer, D. J. (2019). Evaluating effect size in psychological research: Sense and nonsense. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(2), 156--168.

\bibitem[\citeproctext]{ref-Gelman2008-zp}
Gelman, A. (2008). Scaling regression inputs by dividing by two standard deviations. \emph{Statistics in Medicine}, \emph{27}, 2865--2873. \url{https://doi.org/10.1002/sim.3107}

\bibitem[\citeproctext]{ref-gigerenzer2004null}
Gigerenzer, G., Krauss, S., \& Vitouch, O. (2004). The null ritual. \emph{The Sage Handbook of Quantitative Methodology for the Social Sciences}, 391--408.

\bibitem[\citeproctext]{ref-Gross2023-fl}
Groß, J., \& Möller, A. (2023). A note on cohen's d from a partitioned linear regression model. \emph{Journal of Statistical Theory and Practice}, \emph{17}. \url{https://doi.org/10.1007/s42519-023-00323-w}

\bibitem[\citeproctext]{ref-hagen1997praise}
Hagen, R. L. (1997). \emph{In praise of the null hypothesis statistical test.}

\bibitem[\citeproctext]{ref-haig2017tests}
Haig, B. D. (2017). Tests of statistical significance made sound. \emph{Educational and Psychological Measurement}, \emph{77}(3), 489--506.

\bibitem[\citeproctext]{ref-Hedges1981-za}
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{6}, 107--128. \url{https://doi.org/10.3102/10769986006002107}

\bibitem[\citeproctext]{ref-hedges1984estimation}
Hedges, L. V. (1984). Estimation of effect size under nonrandom sampling: The effects of censoring studies yielding statistically insignificant mean differences. \emph{Journal of Educational Statistics}, \emph{9}(1), 61--85.

\bibitem[\citeproctext]{ref-jarke2022roadmap}
Jarke, H., Anand-Vembar, S., Alzahawi, S., Andersen, T. L., Bojanić, L., Carstensen, A., Feldman, G., Garcia-Garzon, E., Kapoor, H., Lewis, S., et al. (2022). A roadmap to large-scale multi-country replications in psychology. \emph{Collabra: Psychology}, \emph{8}(1), 57538.

\bibitem[\citeproctext]{ref-kramer2014experimental}
Kramer, A. D., Guillory, J. E., \& Hancock, J. T. (2014). Experimental evidence of massive-scale emotional contagion through social networks. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{111}(24), 8788.

\bibitem[\citeproctext]{ref-krueger2001null}
Krueger, J. (2001). Null hypothesis significance testing: On the survival of a flawed method. \emph{American Psychologist}, \emph{56}(1), 16.

\bibitem[\citeproctext]{ref-lakens2013calculating}
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}, 62627.

\bibitem[\citeproctext]{ref-lakens2021practical}
Lakens, D. (2021). The practical alternative to the p value is the correctly used p value. \emph{Perspectives on Psychological Science}, \emph{16}(3), 639--648.

\bibitem[\citeproctext]{ref-lakens2022sample}
Lakens, D. (2022). Sample size justification. \emph{Collabra: Psychology}, \emph{8}(1), 33267.

\bibitem[\citeproctext]{ref-miller2017hypothesis}
Miller, J. (2017). Hypothesis testing in the real world. \emph{Educational and Psychological Measurement}, \emph{77}(4), 663--672.

\bibitem[\citeproctext]{ref-morris2002combining}
Morris, S. B., \& DeShon, R. P. (2002). Combining effect size estimates in meta-analysis with repeated measures and independent-groups designs. \emph{Psychological Methods}, \emph{7}(1), 105.

\bibitem[\citeproctext]{ref-moshontz2018psychological}
Moshontz, H., Campbell, L., Ebersole, C. R., IJzerman, H., Urry, H. L., Forscher, P. S., Grahe, J. E., McCarthy, R. J., Musser, E. D., Antfolk, J., et al. (2018). The psychological science accelerator: Advancing psychology through a distributed collaborative network. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.

\bibitem[\citeproctext]{ref-nickerson2000null}
Nickerson, R. S. (2000). Null hypothesis significance testing: A review of an old and continuing controversy. \emph{Psychological Methods}, \emph{5}(2), 241.

\bibitem[\citeproctext]{ref-orben_crud_2020}
Orben, A., \& Lakens, D. (2020). Crud ({Re}){Defined}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(2), 238--247. \url{https://doi.org/10.1177/2515245920917961}

\bibitem[\citeproctext]{ref-Satterthwaite1946-aq}
Satterthwaite, F. E. (1946). An approximate distribution of estimates of variance components. \emph{Biometrics Bulletin}, \emph{2}, 110. \url{https://doi.org/10.2307/3002019}

\bibitem[\citeproctext]{ref-sirois2023pupil}
Sirois, S., Brisson, J., Blaser, E., Calignano, G., Donenfeld, J., Hepach, R., Hochmann, J.-R., Kaldy, Z., Liszkowski, U., Mayer, M., et al. (2023). The pupil collaboration: A multi-lab, multi-method analysis of goal attribution in infants. \emph{Infant Behavior and Development}, \emph{73}, 101890.

\bibitem[\citeproctext]{ref-szucs2017empirical}
Szucs, D., \& Ioannidis, J. P. (2017). Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature. \emph{PLoS Biology}, \emph{15}(3), e2000797.

\bibitem[\citeproctext]{ref-transue2019apa}
Transue, B. (2019). \emph{APA style 7th edition}.

\bibitem[\citeproctext]{ref-Viechtbauer2007-tq}
Viechtbauer, W. (2007). Approximate confidence intervals for standardized effect sizes in the two-independent and two-dependent samples design. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{32}, 39--60. \url{https://doi.org/10.3102/1076998606298034}

\bibitem[\citeproctext]{ref-weiss2014spatial}
Weiss, A. H., Biron, T., Lieder, I., Granot, R. Y., \& Ahissar, M. (2014). Spatial vision is superior in musicians when memory plays a role. \emph{Journal of Vision}, \emph{14}(9), 18--18.

\bibitem[\citeproctext]{ref-Welch1947-wh}
Welch, B. L. (1947). The generalization of {``student's''} problem when several different population variances are involved. \emph{Biometrika}, \emph{34}, 28. \url{https://doi.org/10.2307/2332510}

\bibitem[\citeproctext]{ref-wilson2020science}
Wilson, B. M., Harris, C. R., \& Wixted, J. T. (2020). Science is not a signal detection problem. \emph{Proceedings of the National Academy of Sciences}, \emph{117}(11), 5559--5567.
